Individual and Differential Harm in Redistricting

### 2025-07-25 paper/harm.qmd
move §4 to app

Estimating these quantities from available data is another matter, of course, and requires additional assumptions, as we describe next.

# Estimating the Harm Measures {#sec-estimating}

## Modeling Districting Plans

## Modeling Election Outcomes

## Calculating Harm and Differential Harm

@@

>>>>

Estimating these quantities from available data is another matter, of course, and requires additional assumptions, as we describe in @sec-methods.

@@

# Methods {#sec-methods}

This section discusses estimating the proposed harm measures from real data, and provides details on the analyses conducted for the three applications in the main text.

## Estimating the Harm Measures {#sec-estimating}

### Modeling Districting Plans

### Modeling Election Outcomes

### Calculating Harm and Differential Harm
